run_model_fitting

### 2019-01-11 bda/analysis/fit_model.Rmd
update human-model comparison to be proportions instead of counts (to mirror Kanwals analysis). think about t statistical test for the correlation coefs?

@@

Compare to "optimal baseline" optimal in that `time` condition always pick short, `accuracy` always long, etc.
```{r}
bda_vs_baseline_plot <- df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequenty', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 24,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  gather('model', 'pred', c(baseline, estCnt)) %>%
  mutate(model=ifelse(model=='estCnt', 'BDA', 'Basline')) %>%
  ggplot(aes(x=actualCnt, y=pred, col=condition), alpha=0.4) +
    geom_point(aes(fill=condition), alpha=0.6, size=3, colour="white", pch=21) +
    geom_abline(intercept=0, slope=1, col='grey', alpha=0.4) +
    # geom_point(aes(x=actualInrequentProps, y=estInfrequentProps, col=condition), alpha=0.4) +
    facet_wrap(~model, scales="free") +
    ylab('Baseline model \n counts of short form') +
    xlab('Human data \n counts of short form') +
    theme_few()

@@

```{r}
df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequenty', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 24,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  group_by(condition) %>%
  summarise(r2 = cor(actualCnt, estCnt)^2)

df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequenty', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 24,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  summarise(r2 = cor(actualCnt, baseline))

@@

>>>>

## Counts plot 1

@@

## Counts plot 2

Compare to "optimal baseline" optimal in that `time` condition always pick short, `accuracy` always long, etc.
```{r}
bda_vs_baseline_plot <- df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequent', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 24,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  gather('model', 'pred', c(baseline, estCnt)) %>%
  mutate(model=ifelse(model=='estCnt', 'BDA', 'Baseline')) %>%
  ggplot(aes(x=actualCnt, y=pred, col=condition), alpha=0.4) +
    geom_point(aes(fill=condition, shape=type), alpha=0.6, size=3) +
    geom_abline(intercept=0, slope=1, col='grey', alpha=0.4) +
    # geom_point(aes(x=actualInrequentProps, y=estInfrequentProps, col=condition), alpha=0.4) +
    facet_wrap(~model, scales="free") +
    ylab('Baseline model \n counts of short form') +
    xlab('Human data \n counts of short form') +
    theme_few()

@@

# Proportions Analysis

```{r}
df_cors <- df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequent', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 0,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  gather('model', 'pred', c(baseline, estCnt)) %>%
  group_by(IP, condition, actualCnt, model) %>%
  summarise(cntShortForms=sum(pred)) %>%
  group_by(IP, model, condition) %>%
  summarise(estCnts=sum(cntShortForms),
            actCnts=sum(actualCnt)) %>%
  mutate(condition_n=ifelse(condition=='combined' | condition=='accuracy', 32, 64)) %>%
  mutate(estProp=estCnts/condition_n,
         actProp=actCnts/condition_n) %>%
  ungroup
```

```{r}
df_cors %>%
  group_by(model) %>%
  summarise(n=n(),
            r=cor(estProp, actProp)^2)
```

## Proportions plot1

```{r}
df_cors %>%
  mutate(model=ifelse(model=='baseline', 'Baseline', 'BDA RSA')) %>%
  ggplot(aes(x=actProp, y=estProp, col=condition), alpha=0.4) +
    geom_point(aes(fill=condition), alpha=0.6, size=3) +
    geom_abline(intercept=0, slope=1, col='grey', alpha=0.4) +
    # geom_point(aes(x=actualInrequentProps, y=estInfrequentProps, col=condition), alpha=0.4) +
    facet_wrap(~model) +
    ylab('Baseline model \n counts of short form') +
    xlab('Human data \n counts of short form') +
    ylim(0, 1) +
    xlim(0, 1) +
    theme_few()

ggsave('../../paper/figs/bda-vs-baseline-plot.png', plot = last_plot(), width=6, height=3)
```

Some kind of significance test?

```{r}
fisher.z <- function(r1,r2,n1,n2) {
  # Todo: review (https://stats.stackexchange.com/questions/64152/are-two-pearson-correlation-coefficients-different)
  ((0.5*log((1+r1)/(1-r1)))-(0.5*log((1+r2)/(1-r2))))/((1/(n1-3))+(1/(n2-3)))^0.5
}

@@

```{r}
rs <- df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequent', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 24,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  filter(type=='frequent') %>%
  gather(model, value,  c(estCnt, baseline)) %>%
  select(actualCnt, model, value, condition) %>%
  group_by(model) %>%
  summarise(n=n(),
            r=cor(actualCnt, value)^2)
print(rs)
```
